CONEM2024-0025\\ A NEW EFFECTIVE ABC MULTICRITERIA CLASSIFICATION WITH ANALYTICAL HIERARCHY PROCESS: HOW TO ATTRIBUTE WEIGHTS AND FORCE CONSISTENCY OF PAIRWISE COMPARISONS MATRIX

### 2024-03-18 accepted/CONEM2024/FCPCOM/CONEM2024.tex
minor correction

    To test the methodology proposed in this article, data were collected for construction of the pairwise comparison matrix and for ABC classification, using the billing (bl) criterion and other criteria suggested by \cite{FloresWhybark1986}: lead-time (lt); criticality (cr); obsolescence (ob); commonality (cm); substitutability (sb); and repairability (rp). To collect the data, we partnered with three companies from three different sectors: car mechanics; furniture trades; and plastic packaging manufacturing. Based on the data collected, three benchmarks were developed. The date.txt files corresponding to these three benchmarks are available at https://tbfraga.github.io/COPSolver/ benchmarks/. Appendice A presents the data.txt file elaborated with the data provided by the furniture trades company.

>>>>

    To test the methodology proposed in this article, data were collected for construction of the pairwise comparisons matrix and for ABC classification, using the billing (bl) criterion and other criteria suggested by \cite{FloresWhybark1986}: lead-time (lt); criticality (cr); obsolescence (ob); commonality (cm); substitutability (sb); and repairability (rp). To collect the data, we partnered with three companies from three different sectors: car mechanics; furniture trades; and plastic packaging manufacturing. Based on the data collected, three benchmarks were developed. The date.txt files corresponding to these three benchmarks are available at https://tbfraga.github.io/COPSolver/ benchmarks/. Appendice A presents the data.txt file elaborated with the data provided by the furniture trades company.
